---
title: "CV Sereina Graber"
author:
  firstname: Sereina M.
  lastname: Graber
  address: "Zurich, Switzerland"
  position: "PhD ・Data Scientist ・Researcher"
  summary: " Creative & proactive data scientist with a strong interest in cause and effects of drug usage, leveraging strong analytical and programming skills to generate actionable insights & innovative solutions that enhance patients well-being."
  contacts:
    - icon: fa envelope
      text: sereina.graber@gmail.com
      url: "mailto:sereina.graber@gmail.com"
    - icon: fa star #assets/icon/bi-house-fill.svg
      text: serigra.github.io
      url: https://serigra.github.io/Webpage_Quarto/
    - icon: fa brands github
      text: GitHub
      url: https://github.com/serigra
    - icon: fa brands orcid
      text: 0009-0005-2128-0827
      url: https://orcid.org/0009-0005-2128-0827
    - icon: fa brands researchgate
      text: ResearchGate
      url: https://www.researchgate.net/profile/Sereina-Graber
    - icon: fa brands linkedin
      text: LinkedIn
      url: https://www.linkedin.com/in/sereina-maria-graber-078701bb/
profile-photo: img/foto_SG.jpg
format: awesomecv-typst
---
```{r}
#| output: false
#| echo: false


library(tidyverse)

source("functions.R")
```



::: {.leftpanel}
# Experience

```{=typst}
#resume-entry(
  title: "Data Scientist & Researcher",
  date: "90% | Aug 2019 - current",
  location: "",
  description: "Department of Health Sciences, Helsana Ins. Group, Zurich",
)

```
* Lead, conceptualize and execute scientific studies and analytical projects, e.g.: 
  - Discrepancy between antibiotic pack sizes and guidelines ([[[link to study]{.underline}]{style="color:#23534799;"}](https://link.springer.com/article/10.1007/s15010-024-02420-9))
  - How insurance models affect inappropriate drug prescribing ([[[link to study]{.underline}]{style="color:#23534799;"}](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0311099))
* Development of automated processes to cleanse, aggregate and consolidate diverse
"big data" sources (including `SQL` procedures and `R` software pkgs)
* Data analyses and statistical programming
  - data extraction and processing (using `SQL` and `R`)
  - development and validation of statistical/ machine learning models \
  (a.o.: GLM, GLMM, GEE, RF, survival analyses)
  - visualizations (mainly using `ggplot`, `plotly`, `shiny`)
* Interpret/ present/ discuss results to/ with external/ internal stakeholders and \
collaborate on publishing scientific publications
* Supervision of PhD student and mentoring team members

```{=typst}
#resume-entry(
  title: "Data Scientist",
  date: "100% | Aug 2017 - Jul 2019",
  location: "",
  description: "Advanced Analytics, Sanitas Ins. Group, Zurich",
)
```

* Lead, design and implementation of analytical projects: Data mining &
preparation, analyses & machine learning, preparation of results and discussion
with internal/external stakeholders, project examples:
  - Predictive models for forecasting churn probabilities
  - Development of a chatbot in the area of customer consulting using NLP and
Machine Learning (in collaboration with external consultants)
  - Claim audit system: efficiency testing and further development of rules and
regulations (including implementation of analysis tool in R shiny)
* In-house consulting and teaching of statistical and analytical skills

```{=typst}
#resume-entry(
  title: "Biostatistician",
  date: "diverse projects | Mar 2012 - Jul 2016",
  location: "",
  description: "Institute of Anesthesiology, University Hospital Zürich 
Pneumology and Sleep Medicine, Cantonal Hospital Aarau",
)
```
* Design, implementation of and consulting on statistics and data analyses for 
clinical trials/ scientific publications




# Academic Career

```{=typst}
#resume-entry(
  title: "Ph.D. in Evolutionary Biology",
  date: "Aug 2013 - Jul 2017",
  location: "",
  description: "Anthropological Institute and Museum, University of Zurich",
   top-space: 1.1em,
  below-space-second: 0.3em,
)

#resume-entry(
  title: "Master of Science - Biostatistics",
  date: "Sept 2012 - May 2015",
  location: "",
  description: "Epidemiology, Biostatistics and Prevention Institute, University of Zurich",
  top-space: 1.1em,
  below-space-second: 0.3em, 
)

#resume-entry(
  title: "Master of Science - Biology",
  date: "Sept 2010 - May 2012",
  location: "",
  description: "Anthropological Institute and Museum, University of Zurich",
  top-space: 1.1em,
  below-space-second: 0.3em, 
)

#resume-entry(
  title: "Bachelor of Science - Biology",
  date: "Sept 2007 - May 2010",
  location: "",
  description: "University of Zurich",
  top-space: 1.1em,
  below-space-second: 0.3em, 
)
```
:::

::: {.rightpanel}

# Extracurricular


Member of the organizing committee\
[[[Zurich R User Group!]{.underline}]{style="color:#23534799;"}](https://zurich-r-user-group.github.io/)

# Skills

```{r}
#| echo: false
#| message: false
#| fig-width: 5
#| fig-height: 6

skill_dots(skills <- c("R", "R Shiny", "Quarto", "Python", "SQL", "LaTex", "Git", "Bash/ Shell", "SPSS", "JMP", "MS Office"),
           scores <- c(5, 4, 4, 2, 5, 3, 4, 2, 3, 3, 4) )
```




# Languages

```{r}
#| echo: false
#| message: false
#| fig-width: 5
#| fig-height: 1.5

skill_dots(skills <- c("German", "English", "French"),
          scores <- c(5, 4, 1))
```


# Personal Interests

Programming & visualizing for fun,\
hiking & cycling with my dog



# References

available upon request

:::




